---
title: "Linear Regression Analysis"
author: "Poorvi"
date: "7/11/2020"
output: html_document
---

### Height Weight Chart
x represents Height  and y is the weight of a person
 linear regression equation can be written as
 y = a+ bx
 where y = Response Variable
       x = Predictor Variable
 a,b = Coefficients
 Create the predictor and response variable.
 create a relation model using the lm() function
 Determining the values of coefficients by printing the relationship
 
 
```{r assignment}
x <- c(151, 174, 138, 186, 128, 136, 179, 163, 152, 131)
y <- c(63, 81, 56, 91, 47, 57, 76, 72, 62, 48)
relation <- lm(y~x)
print(relation)
```
 
We can also get the summary of a relationship using the summary function

```{r }
print(summary(relation))
```

Give the chart file a name.
```{r}
png(file = "linearregression.png")

```




Plot the chart

```{r}
plot(y,x,col = "blue",main = "Height & Weight Regression",
     abline(lm(x~y)),cex = 1.3,pch = 16,xlab = "Weight in Kg",ylab = "Height in cm")

```



Save the file

Predicting value of th eresponse variable when the
predictor variable value is given and we have found out the values of Coefficients
Find weight of a person with height 170

```{r save file}
a <- data.frame(x = 170)
result <-  predict(relation,a)
print(result)
```

